Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-27 GEMDataSource.Rmd
Imported, cleaned, and began merging new GEM data

GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)

Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]

names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))

@@

@@

@@

# Run linear regression R1
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

@@

# Run linear regression R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

@@

>>>>

GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)

@@

### Clean GEM NES Datasets
# Draw out Country and D01 only
Clean01 <- GEM2001[,c("country", "ki01d01")]
Clean02 <- GEM2002[,c("country", "ki02d01")]
Clean03 <- GEM2003[,c("country", "ki03d01")]
Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]

remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)

# Edit column names for each dataframe
names(Clean01) <- gsub("ki01d01", "2001", names(Clean01))
names(Clean01) <- gsub("country", "Country", names(Clean01))
names(Clean02) <- gsub("ki02d01", "2002", names(Clean02))
names(Clean02) <- gsub("country", "Country", names(Clean02))
names(Clean03) <- gsub("ki03d01", "2003", names(Clean03))
names(Clean03) <- gsub("country", "Country", names(Clean03))
names(Clean04) <- gsub("ki04d01", "2004", names(Clean04))
names(Clean04) <- gsub("ki04ctry", "Country", names(Clean04))
names(Clean05) <- gsub("KI05D01", "2005", names(Clean05))
names(Clean05) <- gsub("KI05ctry", "Country", names(Clean05))
names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
names(Clean06) <- gsub("KI06CTRY", "Country", names(Clean06))
names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
names(Clean07) <- gsub("ki07ctry", "Country", names(Clean07))
names(Clean08) <- gsub("NES08_D01_MEAN", "2008", names(Clean08))
names(Clean08) <- gsub("NES08COUNTRY", "Country", names(Clean08))
names(Clean09) <- gsub("NES09_D01_MEAN", "2009", names(Clean09))
names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
names(Clean10) <- gsub("NES10_D01_MEAN", "2009", names(Clean10))
names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))

@@

# Merge GEMNES country level data
Merged1 <- merge(Clean01, Clean02,
                   union("Country")
                   all = TRUE)

# Grab the rows we need
myvars <- c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States")

NewData <- Data[myvars, 1]

@@

# Run linear regression R1
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)

@@

# Run linear regression R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)

@@

Estonia
Luxemburg
Slovak Republic
